---
title: "Descriptive Statistics, Bivariate Correlations, and Reliability Coefficients"
author: "Zachary Himmelberger"
output:
  pdf_document: default
  html_document: default
---

# Import Packages

```{r}
library(psych)
```

# Import Data

```{r}
source("Data-Processing.R")
```

# Descriptive Statistics

For the participant section. 

``` {r}
describe(analysis.df$age)
table(analysis.df$gender)
table(analysis.df$ethnicity)
```

Descriptive statistics for Table 1. 

``` {r}
describe(analysis.df$attitude)
describe(analysis.df$social.desirability)
describe(analysis.df$quantity)
describe(analysis.df$quality)
describe(analysis.df$knowledge)
describe(analysis.df$openness)
describe(analysis.df$conscientiousness)
describe(analysis.df$extroversion)
describe(analysis.df$agreeableness)
describe(analysis.df$neuroticism)
```

# Bivariate Correlations

Correlations for Table 2. Note that all correlations above .132 are significant at the .05 level and all correlations above .173 are significant at the .01 level.

``` {r}
analysis.df %>%
  select(attitude, social.desirability, quantity, quality, 
         knowledge, openness, conscientiousness, extroversion,
         agreeableness, neuroticism) %>%
  cor() %>%
  round(digits=2)
```

# Reliability Coefficients

Cronbach's alpha for each scale.

``` {r}
chronbach.df <- raw.df %>%
  drop_na(attitude, social.desirability, openness,
                       conscientiousness, extroversion, agreeableness, neuroticism,
                       quantity, quality, knowledge)
```

## BFI subscales

Openness = .74

```{r}
chronbach.df %>%
  select(BFI_5, BFI_10, BFI_15, BFI_20, 
         BFI_25, BFI_30, BFI_35.r, BFI_40, 
         BFI_41.r, BFI_44) %>%
  psych::alpha()
```

Conscientiousness = .76

```{r}
chronbach.df %>%
  select(BFI_3, BFI_8.r, BFI_13, BFI_18.r, 
         BFI_23.r, BFI_28, BFI_33, BFI_38, 
         BFI_43.r) %>%
  psych::alpha()
```

Extroversion = .86

```{r}
chronbach.df %>%
  select(BFI_1, BFI_6.r, BFI_11, BFI_16, 
         BFI_21.r, BFI_26, BFI_31.r, BFI_36) %>%
  psych::alpha()
```

Agreeableness = .78

```{r}
chronbach.df %>%
  select(BFI_2.r, BFI_7, BFI_12.r, BFI_17, 
         BFI_22, BFI_27.r, BFI_32, BFI_37.r, 
         BFI_42) %>%
  psych::alpha()
```

Neuroticism = .82

```{r}
chronbach.df %>%
  select(BFI_4, BFI_9.r, BFI_14, BFI_19, 
         BFI_24.r, BFI_29, BFI_34.r, BFI_39) %>%
  psych::alpha()
```

## MRAI-R (Attitudes)

Overall = .88

```{r}
chronbach.df %>%
  select(Attitudes_1.r, Attitudes_2, Attitudes_3,
         Attitudes_4.r, Attitudes_5, Attitudes_6.r,
         Attitudes_7.r, Attitudes_8, Attitudes_9.r,
         Attitudes_10.r, Attitudes_11, Attitudes_12.r,
         Attitudes_13.r, Attitudes_14, Attitudes_15.r,
         Attitudes_16.r, Attitudes_17, Attitudes_18.r,
         Attitudes_19, Attitudes_20.r, Attitudes_21.r,
         Attitudes_22.r, Attitudes_23.r, Attitudes_24,
         Attitudes_25.r, Attitudes_26.r, Attitudes_27.r,
         Attitudes_28, Attitudes_29) %>%
  psych::alpha()
```

Integration-segregation = .77

```{r}
chronbach.df %>%
  select(Attitudes_1.r, Attitudes_2, Attitudes_7.r, Attitudes_13.r, 
         Attitudes_17, Attitudes_23.r, Attitudes_29) %>%
  psych::alpha()
```

Social distance = .77

```{r}
chronbach.df %>%
  select(Attitudes_3, Attitudes_5, Attitudes_11, Attitudes_15.r,
         Attitudes_18.r, Attitudes_19, Attitudes_24, Attitudes_27.r) %>%
  psych::alpha()
```

Private rights = .58

```{r}
chronbach.df %>%
  select(Attitudes_6.r, Attitudes_8, Attitudes_12.r, Attitudes_14,
         Attitudes_20.r, Attitudes_22.r, Attitudes_28) %>%
  psych::alpha()
```

Subtle derogatory beliefs = .64

```{r}
chronbach.df %>%
  select(Attitudes_4.r, Attitudes_9.r, Attitudes_10.r, Attitudes_16.r, 
         Attitudes_21.r, Attitudes_25.r, Attitudes_26.r) %>%
  psych::alpha()
```

## Contact and Knowledge

Quality of contact = .89

```{r}
chronbach.df %>%
  select(Quality_2, Quality_3, Quality_4,
         Quality_5, Quality_6, Quality_7.r, Quality_8.r) %>%
  psych::alpha()
```

Quantity of contact = .78

```{r}
chronbach.df %>%
  select(Quantity_1, Quantity_2, Quantity_3, Quantity_4.r,
         Quantity_5, Quantity_6, Quantity_7, Quantity_8,
         Quantity_9, Quantity_10) %>%
  psych::alpha()
```

Knowledge = .90

```{r}
chronbach.df %>%
  select(Knowledge_1, Knowledge_2, Knowledge_3, Knowledge_4,
         Knowledge_5, Knowledge_6, Knowledge_7, Knowledge_8,
         Knowledge_9.r, Knowledge_10, Knowledge_11.r, Knowledge_12,
         Knowledge_13, Knowledge_14, Knowledge_15, Knowledge_16) %>%
  psych::alpha()
```