---
title: "Main Analyses"
author: "Zachary Himmelberger"
output:
  pdf_document: default
  html_document: default
---

# Import Packages

```{r}
library(ppcor)
library(lavaan)
```

# Import Data

```{r}
source("Data-Processing.R")
```

# Linear Regression of Substantive Predictors on MRAI-R Total Scores

We will start by subsetting the data to only include the predictors, then fitting the model. 

```{r}
regression.model.df <- analysis.df %>%
  select(attitude, gender.male, gender.non.binary, non.white, social.desirability.c,
         quantity.c, quality.c, knowledge.c, openness.c, 
         conscientiousness.c, extroversion.c, agreeableness.c, neuroticism.c)

regression.model <- lm(attitude ~ ., data = regression.model.df)
```

Plot the model assumptions. 

``` {r}
plot(regression.model)
```

The model assumptions appear to be reasonable. Now we can look at the model coefficients.

```{r}
summary(regression.model)
```

Let's look at the standardized predictors to see the relative strength of each predictor. 

```{r}
# create a temporary DataFrame to standardize quantitative predictors
temp2 <- df %>%
  select(social.desirability, openness, conscientiousness, extroversion,
         agreeableness, neuroticism,  quantity, quality,
         knowledge) %>%
  scale(center=TRUE, scale=TRUE)

# add a .s after the name of each predictor to identify it as standardized
temp2 <- as.data.frame(temp2, row.names = NULL)
temp2 <- set_names(temp2, paste0(names(temp2), ".s"))

# merge dataframes and recode gender and ethnicity 
standardized.df <- df %>%
  mutate(male = recode(gender,
                       "male" = 1,
                       .default = 0)) %>%
  mutate(non.white = recode(ethnicity,
                       "white" = 0,
                       .default = 1)) %>%
  select(gender, attitude, male, non.white) %>%
  bind_cols(temp2) %>%
  filter(gender != "non-binary") %>%
  drop_na(attitude, social.desirability.s, openness.s,
                       conscientiousness.s, extroversion.s, agreeableness.s, neuroticism.s,
                       quantity.s, quality.s, knowledge.s)

# create the new dataframes with the standardized predictors
standardized.regression.model.df <- standardized.df %>%
  select(attitude, male, non.white, social.desirability.s,
         quantity.s, quality.s, knowledge.s, openness.s, 
         conscientiousness.s, extroversion.s, agreeableness.s, neuroticism.s)

# fit the model
standardized.regression.model <- lm(attitude ~ ., data = standardized.regression.model.df)

# examine model coefficients
summary(standardized.regression.model)
```

Finally, we can look at the partial correlations for each predictor. 

```{r}
pcor(regression.model.df)
```


# Mediation Model

We will create the mediation model and fit it to the data. 

``` {r}
# set seed for reproducibility
set.seed(760120)

med_model <- '
  # direct effects
  quality ~ b1 * openness + b2 * agreeableness
  attitude ~ b3 * openness + b4 * agreeableness + b5 * quality
  # indirect effects
  indirect_openness := b1 * b5
  indirect_agreeableness := b2 * b5
  # total effects
  total_openness := b3 + (b1 * b5)
  total_agreeableness := b4 + (b2 * b5)
'

med_model_fit <- sem(med_model, data = analysis.df,
                         se = "bootstrap", bootstrap = 10000)
```

Examine the overall model fit. 

```{r}
inspect(med_model_fit, "r2")
```

Examine the unstandardized model coefficients. 

```{r}
summary(med_model_fit, fit.measures=TRUE, ci=TRUE)
```

Examine the standardized model coefficients.

```{r}
summary(med_model_fit, fit.measures=TRUE, ci=TRUE, standardized = TRUE)
```
